Response to the defense feedback

### 2021-06-19 Chapter-7/Chapter-7.tex
Updates from Overleaf

\textbf{Side-channel Leakage Quantification from Noisy Observations.} It is possible to extend the quantification part to include other side-channel
signals (e.g., sound, CPU usages, EM signals). The key is to model the noises
properly. In this dissertation, we assume that an attacker can have a noise-free
observation. While a noise-free observation is possible for some address-based
side-channel attacks, the assumption is still too ideal for many real side-channel
attacks. The good news is that there are some mature methods in information theory to model some types of noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a
computable method to estimate the information that can be reliably transferred over a channel between the secret data and attackers' observations.

>>>>

\textbf{Side-channel Leakage Quantification from Noisy Observations.} It is possible to extend the quantification part to include other side-channel
signals (e.g., sound, CPU usages, EM signals). The key is to model the noises
properly. In this dissertation, we assume that an attacker can have a noise-free
observation. While a noise-free observation is possible for some address-based
side-channel attacks, the assumption is still too ideal for many real side-channel
attacks. The good news is that there are some mature methods in information theory to model some types of noises (e.g., Gaussian noise). The noisy-channel coding theorem~\cite{shannon1948mathematical} provides a
computable method to estimate the information that can be reliably transferred over a channel between the secret data and attackers' observations.
